---
title: "Extra Plots"
output: html_document
---

```{r packages, include = FALSE}

# List of required packages
required_packages <- c("sf", "tidyverse")

# Function to check and install missing packages
install_missing_packages <- function(packages) {
  new_packages <- packages[!(packages %in% installed.packages()[,"Package"])]
  if(length(new_packages)) install.packages(new_packages, dependencies = TRUE)
}

# Install any missing packages
install_missing_packages(required_packages)

# Load the packages
lapply(required_packages, require, character.only = TRUE)

```

```{r load data}

pm <- read.csv("pm_per_station_imputed.csv")
Mashhad_shape <- read_sf("mashhad_shape")
district_data <- read.csv("district_data_final.csv")

dir.create("plots")

```


```{r manipulate data}
Sys.setlocale("LC_ALL","English")

district_data$DOW <- weekdays(as.Date(district_data$date))

district_data <- district_data %>% mutate(
  month = as.factor(month),
  districtID = as.factor(districtID),
  date = as.Date(date),
  DOW = as.factor(DOW)
)
district_data <- district_data %>%
  group_by(districtID) %>%
  mutate(
    PM2.5_lag1 = lag(PM2.5, 1),
    PM2.5_lag2 = lag(PM2.5, 2),
    PM2.5_lag3 = lag(PM2.5, 3),
    PM2.5_lag4 = lag(PM2.5, 4),
    PM2.5_lag5 = lag(PM2.5, 5),
    PM2.5_cum1 = (PM2.5 + lag(PM2.5, 1)) / 2,
    PM2.5_cum2 = (PM2.5 + lag(PM2.5, 1) + lag(PM2.5, 2)) / 3,
    PM2.5_cum3 = (PM2.5 + lag(PM2.5, 1) + lag(PM2.5, 2) + lag(PM2.5, 3)) / 4,
    PM2.5_cum4 = (PM2.5 + lag(PM2.5, 1) + lag(PM2.5, 2) + lag(PM2.5, 3) + lag(PM2.5, 4)) / 5,
    PM2.5_cum5 = (PM2.5 + lag(PM2.5, 1) + lag(PM2.5, 2) + lag(PM2.5, 3) + lag(PM2.5, 4) + lag(PM2.5, 5)) / 6
  ) %>%
  ungroup()

district_data$pop_above_age65 <- c(
  ((district_data$population * district_data$percent_age65) / 100))
district_data$pop_below_age65 <- district_data$population - district_data$pop_above_age65

# without deletion of first 5 days due to lag computation
district_data_noNA <- district_data 

district_data <- district_data[complete.cases(district_data),]

```



# Map of Mashhad with AQM-Stations
```{r}
ggplot() +
  geom_sf(data = Mashhad_shape, fill = "white", color = "black") +
  geom_point(data = pm, aes(x = Xcoor, y = Ycoor), size = 6, color = "red") +  
  geom_text(data = pm, aes(x = Xcoor, y = Ycoor, label = stationID), 
            nudge_y = 600,  
            size = 6, check_overlap = TRUE, hjust = "center", vjust = 0) +
  labs( x = NULL, y = NULL)+
  theme_minimal()+
  theme(
    axis.text = element_text(size = 18),  
    axis.title = element_text(size = 20),
    plot.title = element_text(size = 26)
  )



ggsave("plots/map_mashhad.png", width = 10, height = 10)

```

# Map of Mashhad
```{r}

ggplot() +
  geom_sf(data = Mashhad_shape, fill = "white", color = "black") +
  labs(title = "Map of Mashhad")+
  theme_minimal()+
  theme(
    axis.text = element_text(size = 18),  
    axis.title = element_text(size = 20),
    plot.title = element_text(size = 26)
  )

ggsave("plots/map_mashhad_woAQM.png", width = 10, height = 10)
```

# Histogram CVD
```{r}

mean_cvd <- mean(district_data_noNA$CVD, na.rm = TRUE)

ggplot(district_data_noNA, aes(x = CVD)) +
  geom_histogram(fill = "grey", color = "black", binwidth = 1) +
  geom_vline(xintercept = mean_cvd, color = "red", linetype = "dashed", size = 1) +
  annotate("text", x = mean_cvd + 1.1, y = Inf, 
           label = paste("Mean:", round(mean_cvd, 2)), 
           vjust = 2, color = "red", size = 6) +
  labs( 
       x = "CVD Hospitalizations per District and Date", 
       y = "Frequency") +
  theme_minimal()+
  theme(
    axis.text = element_text(size = 18), 
    axis.title = element_text(size = 20),
    legend.text = element_text(size = 18),
    legend.title = element_text(size = 20),
    plot.title = element_text(size = 26)
    )

ggsave("plots/hist_cvd.png", width = 20, height = 10)

```


# Monthly aggregated time series of CVD
```{r}
district_data_co_sc <- district_data %>%
  mutate(month_year = floor_date(date, "month")) %>%
  group_by(month_year) %>%
  summarise(CVD = sum(CVD))

covid_periods <- district_data_noNA %>%
  filter(covid == 1) %>%
  summarise(start = min(date), end = max(date))

screening_periods <- district_data_noNA %>%
  filter(screening == 1) %>%
  summarise(start = min(date), end = max(date))

ggplot(district_data_co_sc, aes(x = month_year, y = CVD)) +
  geom_rect(data = covid_periods, inherit.aes = FALSE,
            aes(xmin = start, xmax = end, ymin = -Inf, ymax = Inf),
            fill = "blue", alpha = 0.2) +
  annotate("text", label = "Covid", x = as.Date("2020-08-30"),
           y = Inf, vjust = 2, color = "blue", size = 8) +
  geom_rect(data = screening_periods, inherit.aes = FALSE,
            aes(xmin = start, xmax = end, ymin = -Inf, ymax = Inf),
            fill = "red", alpha = 0.2) +
  annotate("text", label = "Screening", x = as.Date("2019-09-15"),
           y = Inf, vjust = 2, color = "red", size = 8) +
  geom_line() +  
  geom_point() +  
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y") +
  labs( x = "Time", y = "Number of CVD Hospitalizations") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 18),
    axis.text = element_text(size = 18), 
    axis.title = element_text(size = 20),
    legend.text = element_text(size = 18),
    legend.title = element_text(size = 20),
    plot.title = element_text(size = 26)
  )+
  ylim(0, NA)


ggsave("plots/monthly_cvd.png", width = 20, height = 10)
```

# Mean PM2.5 across districts
```{r}

pm_mean_per_district <- district_data_noNA %>%
  group_by(districtID) %>%
  summarise(MeanPM25 = mean(PM2.5, na.rm = TRUE)) %>%
  mutate(districtID = as.integer(districtID))

Mashhad_shape_with_pm <- Mashhad_shape %>%
  left_join(pm_mean_per_district, by = c('District' = 'districtID'))

ggplot(Mashhad_shape_with_pm) +
  geom_sf(aes(fill = MeanPM25), color = "black", size = 0.25) +
  scale_fill_gradient(low = "grey90", high = "red", name = "Mean PM2.5",
                      limits = c(23, 50), oob = scales::oob_squish)+  
  theme_minimal()+
  theme(
    axis.text = element_text(size = 18), 
    axis.title = element_text(size = 20),
    legend.text = element_text(size = 18),
    legend.title = element_text(size = 20),
    plot.title = element_text(size = 20)
    )

ggsave("plots/map_mashhad_pm.png", width = 10, height = 10)


```

# Mean PM2.5 across stations
```{r}

pm_mean_per_station <- pm %>%
  group_by(stationID, Xcoor, Ycoor) %>%
  summarise(MeanPM25 = mean(PM2.5, na.rm = TRUE)) %>%
  mutate(stationID = as.integer(stationID)) %>% ungroup()


ggplot() +
  geom_sf(data = Mashhad_shape, fill = "white", color = "black") +
  geom_point(data = pm_mean_per_station, 
             aes(x = Xcoor, y = Ycoor, fill = MeanPM25), size = 6, 
             shape = 21, color = "black") +
  scale_fill_gradient(low = "grey90", high = "red", name = "Mean PM2.5",
                      limits = c(23, 50), oob = scales::oob_squish) +
  labs(  x = NULL, y = NULL) +
  theme_minimal()+
  theme(
    axis.text = element_text(size = 18), 
    axis.title = element_text(size = 20),
    legend.text = element_text(size = 18),
    legend.title = element_text(size = 20),
    plot.title = element_text(size = 20)
    )


ggsave("plots/map_mashhad_pm_station.png", width = 10, height = 10)

```

# Schematic grid on Map
```{r}

bbox <- st_bbox(Mashhad_shape)
x_seq <- seq(bbox["xmin"], bbox["xmax"], by = 2000)
y_seq <- seq(bbox["ymin"], bbox["ymax"], by = 2000)
grid_points <- expand.grid(X = x_seq, Y = y_seq)
grid_sf <- st_as_sf(grid_points, coords = c("X", "Y"), 
                    crs = st_crs(Mashhad_shape))

ggplot() +
  geom_sf(data = Mashhad_shape, fill = "white", color = "black") +
  geom_sf(data = st_boundary(Mashhad_shape), color = "black", size = 0.5) +
  geom_sf(data = grid_sf, aes(color = "Grid Points", shape = "Grid Points"), 
          size = 3) +
  geom_point(data = pm, aes(x = Xcoor, y = Ycoor, 
                            color = "AQM-Stations", shape = "AQM-Stations"), 
             size = 4) +
  scale_color_manual(
    values = c("Grid Points" = "black", "AQM-Stations" = "red"),
    name = "Point Type",
    labels = c("AQM-Stations" = "AQM-Stations", "Grid Points" = "Grid Points")  
  ) +
  scale_shape_manual(
    values = c("Grid Points" = 16, "AQM-Stations" = 15), 
    name = "Point Type",
    labels = c("AQM-Stations" = "AQM-Stations", "Grid Points" = "Grid Points") 
  ) +
  theme_minimal() +
  theme(
    axis.text = element_text(size = 18), 
    axis.title = element_text(size = 20),
    legend.text = element_text(size = 18),
    legend.title = element_blank(),
    plot.title = element_text(size = 20),
        legend.position = "bottom" 

  ) +
  labs(
    x = NULL, y = NULL)

ggsave("plots/map_grid.png", width = 10, height = 10)

```

# Histogram imputed and aggregated PM2.5 values
```{r}

ggplot(district_data_noNA, aes(x = PM2.5)) +
  geom_histogram(binwidth = 5, fill = "grey", color = "black",
                 breaks = seq(0, 300, by = 5)) +
  geom_vline(aes(xintercept = 15), linetype = "dashed", color = "red", size = 1) +
  annotate("text", x = 60, y = Inf, 
           label = "WHO recommended maximum value (15 µg/m³)", 
           vjust = 2, color = "red", size = 6) +
  labs(
     x = "PM2.5 Value",
     y = "Frequency") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 18), 
    axis.text.y = element_text(size = 18),
    axis.title = element_text(size = 20),
    legend.text = element_text(size = 18),
    legend.title = element_text(size = 20),
    plot.title = element_text(size = 20)
  )

ggsave("plots/hist_pm25_district.png", width = 20, height = 10)

```


# Barplot DistrictID - CVD
```{r}

CVD_district <- district_data_noNA %>%
  group_by(districtID) %>%
  summarise(Mean_CVD = mean(CVD, na.rm = TRUE))

ggplot(CVD_district, aes(x = districtID, y = Mean_CVD)) +
  geom_bar(stat = "identity", fill = "darkgrey") +
  labs(x = "District ID", 
       y = "Mean CVD Cases") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 18), 
    axis.text.y = element_text(size = 18),
    axis.title = element_text(size = 20),
    legend.text = element_text(size = 18),
    legend.title = element_text(size = 20),
    plot.title = element_text(size = 20)
  )+
  ylim(NA, 6.5)

ggsave("plots/CVD_district.png", width = 10, height = 10)


```

# Barplot DOW - CVD
```{r}

CVD_dow <- district_data_noNA %>%
  mutate(DOW = factor(DOW, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))) %>%
  group_by(DOW) %>%
  summarise(Mean_CVD = mean(CVD, na.rm = TRUE))

ggplot(CVD_dow, aes(x = DOW, y = Mean_CVD)) +
  geom_bar(stat = "identity", fill = "darkgrey") +
  labs(x = "Day of the Week", 
       y = "Mean CVD Cases") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 18), 
    axis.text.y = element_text(size = 18),
    axis.title = element_text(size = 20),
    legend.text = element_text(size = 18),
    legend.title = element_text(size = 20),
    plot.title = element_text(size = 20)
  )+
  ylim(NA, 6.5)

ggsave("plots/CVD_dow.png", width = 10, height = 10)

```


# Barplot holiday - CVD

```{r}
CVD_holiday <- district_data_noNA %>%
  mutate(holiday = factor(holiday)) %>%
  group_by(holiday) %>%
  summarise(Mean_CVD = mean(CVD, na.rm = TRUE))

ggplot(CVD_holiday, aes(x = holiday, y = Mean_CVD)) +
  geom_bar(stat = "identity", fill = "darkgrey") +
  labs(x = "Holiday", 
       y = "Mean CVD Cases") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 18), 
    axis.text.y = element_text(size = 18),
    axis.title = element_text(size = 20),
    legend.text = element_text(size = 18),
    legend.title = element_text(size = 20),
    plot.title = element_text(size = 20)
  )+
  ylim(NA, 6.5)

ggsave("plots/CVD_holiday.png", width = 10, height = 10)
```

# Barplot covid - CVD
```{r}

CVD_covid <- district_data_noNA %>%
  mutate(covid = factor(covid)) %>%
  group_by(covid) %>%
  summarise(Mean_CVD = mean(CVD, na.rm = TRUE))

ggplot(CVD_covid, aes(x = covid, y = Mean_CVD)) +
  geom_bar(stat = "identity", fill = "darkgrey") +
  labs(x = "COVID", 
       y = "Mean CVD Cases") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 18), 
    axis.text.y = element_text(size = 18),
    axis.title = element_text(size = 20),
    plot.title = element_text(size = 20)
  )+
  ylim(NA, 6.5)


ggsave("plots/CVD_covid.png", width = 10, height = 10)

```


# Barplot Screening - CVD
```{r}

CVD_screening <- district_data_noNA %>%
  mutate(screening = factor(screening)) %>%
  group_by(screening) %>%
  summarise(Mean_CVD = mean(CVD, na.rm = TRUE))

ggplot(CVD_screening, aes(x = screening, y = Mean_CVD)) +
  geom_bar(stat = "identity", fill = "darkgrey") +
  labs(x = "Screening", 
       y = "Mean CVD Cases") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 18), 
    axis.text.y = element_text(size = 18),
    axis.title = element_text(size = 20),
    plot.title = element_text(size = 20)
  )+
  ylim(NA, 6.5)


ggsave("plots/CVD_screening.png", width = 10, height = 10)

```

# Visualization Weight with distances for aggregation
```{r}

estimated_decay_rate <- 0.0007413299
  
distances <- seq(0, 10000, by = 10)  
weights <- exp(-estimated_decay_rate * distances)

data_for_plot <- data.frame(Distances = distances, Weights = weights)

ggplot(data_for_plot, aes(x = Distances, y = Weights)) +
  geom_line() + 
  labs(
       x = "Distance in Meter",
       y = "Weight") +
  theme_minimal()+
  theme(
    axis.text = element_text(size = 18), 
    axis.title = element_text(size = 20),
    legend.text = element_text(size = 18),
    legend.title = element_text(size = 20),
    plot.title = element_text(size = 26)
    )

ggsave("plots/weights_decay.png", width = 15, height = 10)

```

