---
title: "Modeling"
output: html_document
---

# Warning: long run time 

```{r packages, include = FALSE}

# List of required packages
required_packages <- c("tidyverse", "mgcv", "forecast", "gamlss", "xtable", "gridExtra", "sf")

# Function to check and install missing packages
install_missing_packages <- function(packages) {
  new_packages <- packages[!(packages %in% installed.packages()[,"Package"])]
  if(length(new_packages)) install.packages(new_packages, dependencies = TRUE)
}

# Install any missing packages
install_missing_packages(required_packages)

# Load the packages
lapply(required_packages, require, character.only = TRUE)

dir.create("tables")
dir.create("plots")

set.seed(42)

```

# load and manipulate data
```{r}

Sys.setlocale("LC_ALL","English")


district_data <- read.csv("district_data_final.csv")

district_data$DOW <- weekdays(as.Date(district_data$date))

district_data <- district_data %>% mutate(
  month = as.factor(month),
  districtID = as.factor(districtID),
  date = as.Date(date),
  DOW = as.factor(DOW)
)
district_data <- district_data %>%
  group_by(districtID) %>%
  mutate(
    PM2.5_lag1 = lag(PM2.5, 1),
    PM2.5_lag2 = lag(PM2.5, 2),
    PM2.5_lag3 = lag(PM2.5, 3),
    PM2.5_lag4 = lag(PM2.5, 4),
    PM2.5_lag5 = lag(PM2.5, 5),
    PM2.5_cum1 = (PM2.5 + lag(PM2.5, 1)) / 2,
    PM2.5_cum2 = (PM2.5 + lag(PM2.5, 1) + lag(PM2.5, 2)) / 3,
    PM2.5_cum3 = (PM2.5 + lag(PM2.5, 1) + lag(PM2.5, 2) + lag(PM2.5, 3)) / 4,
    PM2.5_cum4 = (PM2.5 + lag(PM2.5, 1) + lag(PM2.5, 2) + lag(PM2.5, 3) + lag(PM2.5, 4)) / 5,
    PM2.5_cum5 = (PM2.5 + lag(PM2.5, 1) + lag(PM2.5, 2) + lag(PM2.5, 3) + lag(PM2.5, 4) + lag(PM2.5, 5)) / 6
  ) %>%
  ungroup()

district_data$pop_above_age65 <- c(
  ((district_data$population * district_data$percent_age65) / 100))

district_data$pop_below_age65 <- 
  district_data$population - district_data$pop_above_age65

district_data <- district_data[complete.cases(district_data),]

```

# formulas
```{r}

formulaCVD <- as.formula(
  CVD ~ PM2.5 + districtID + DOW + ns(date, 20) + covid + screening + holiday +
    offset(log(population))
)

shortformulaCVD <- '+ districtID + DOW + ns(date, 20) + covid + screening + holiday + offset(log(population))'

shortformulaCVD_wodis <- ' + DOW + ns(date, 20) + covid + screening + holiday + offset(log(population))'

shortformulaCVD_wodate <- '+ districtID + DOW + covid + screening + holiday + offset(log(population)) +'

shortformulaCVD_group<- '+ districtID + DOW + ns(date, 20) + covid + screening + holiday + '

shortformulaCVD_wodis2 <- '+ percent_illiterate + percent_unemployment + percent_age65+ area_km + DOW + ns(date, 20) + covid + screening + holiday +offset(log(population))'


```


# Fit quasipoisson model with PM2.5_lag0 for overdispersion
```{r}
model_qp <- gam(formulaCVD, data = district_data, family = "quasipoisson")

summary(model_qp)

```

# Diagnostic plots for poisson model with PM2.5_lag0 and PM2.5_lag1
```{r}

lag0model <- gamlss(formulaCVD, data = district_data, family = PO)

formulaCVDlag1 <- as.formula(
  CVD ~ PM2.5_lag1 + districtID + DOW + ns(date, 20) + covid + screening + holiday +
    offset(log(population))
)


png("plots/diaglag0.png", width = 10*600, height = 10*300, res = 300)

par(cex.main = 2.5,
    cex.lab = 2,
    cex.axis = 2)
plot(lag0model, 
     parameters = par(mfrow = c(2, 2), 
                      mar = par("mar") + c(0, 1, 0, 0), 
                      bg = "white", col = "black"),
     summaries = FALSE)

dev.off()


lag1model <-  gamlss(formulaCVDlag1, data = district_data, family = PO)


png("plots/diaglag1.png", width = 10*600, height = 10*300, res = 300)

par(cex.main = 2.5,
    cex.lab = 2,
    cex.axis = 2)
plot(lag1model, 
     parameters = par(mfrow = c(2, 2), 
                      mar = par("mar") + c(0, 1, 0, 0), 
                      bg = "white", col = "black"),
     summaries = FALSE)

dev.off()

```

# PACF Plots for PM2.5_lag0 
```{r}

district_data_residuals <- district_data
district_data_residuals$residuals <- resid(lag0model, type = "simple")

plot_and_save_pacf <- function(districtID, data) {
  data_dis <- data[data$districtID == districtID,]
  file_name <- sprintf("plots/pacf_district_lag0_%d.png", districtID)
  
  png(file_name, width = 1000, height = 1000, res = 300) 
  Pacf(data_dis$residuals, plot = TRUE, main = paste("District", districtID), 
       ylim = c(-0.15, 0.15))
  dev.off()
}

for(i in 1:13) {
  plot_and_save_pacf(i, district_data_residuals)
}


```


# Main Models
```{r}

pm2.5_cols <- grep("PM2\\.5", names(district_data), value = TRUE)

df_res <- data.frame(
  variable = character(),
  coefficient = numeric(),
  std.error = numeric(),
  p_value = numeric(),
  AIC = numeric(),
  stringsAsFactors = FALSE
)


for (i in seq_along(pm2.5_cols)) {
  # Define the formula with the current PM2.5 term
  formulaCVD <- as.formula(paste0("CVD ~ ", pm2.5_cols[i], shortformulaCVD))
  
  # Fit model
  model_fit <- gamlss(formulaCVD, data = district_data, family = PO)
  
  model_summary <- summary(model_fit, save = T)
  
  df_res[i, "variable"] <- pm2.5_cols[i]
  df_res[i, "coefficient"] <- model_summary$coef[pm2.5_cols[i]]
  df_res[i, "std.error"] <- model_summary$se[pm2.5_cols[i]]
  df_res[i, "p_value"] <- model_summary$pvalue[pm2.5_cols[i]]
  df_res[i, "AIC"] <- model_fit$aic
  
}


table_df_res <- tableGrob(df_res, rows = NULL)
ggsave("tables/table_df_res.png", table_df_res)

```

# Visualization main results
```{r}

df_res$RR <- exp(df_res$coefficient)
df_res$lower <- exp(df_res$coefficient - 1.96 * df_res$std.error)
df_res$upper <- exp(df_res$coefficient + 1.96 * df_res$std.error)

# Filter for single lag terms
df_lags <- df_res
df_lags[1, 1] <- "PM2.5_lag0"
df_lags <- df_lags[grep("lag", df_lags$variable),]

df_lags$lag_number <- as.numeric(gsub("PM2.5_lag", "", df_lags$variable))


ggplot(df_lags, aes(x = lag_number, y = RR)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .1, size = 1) +
  xlab("Lag") +
  ylab("Relative Risk") +
  scale_x_continuous(breaks = df_lags$lag_number) +
  geom_line(aes(y = 1), color = "red", lty = "dotted", size = 2 )  +
  ylim(1 - 0.0018, 1 + 0.0018) +  
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 18), 
    axis.text.y = element_text(size = 18),
    axis.title = element_text(size = 20),
    legend.text = element_text(size = 18),
    legend.title = element_text(size = 20),
    plot.title = element_text(size = 20)
  )

ggsave("plots/plot_lags.png", width = 10, height = 10)


# Filter for cumulative lag terms
df_cum <- df_res
df_cum[1, 1] <- "PM2.5_cum0"
df_cum <- df_cum[grep("cum", df_cum$variable),]

df_cum$cum_number <- as.numeric(gsub("PM2.5_cum", "", df_cum$variable))


ggplot(df_cum, aes(x = cum_number, y = RR)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .1, size = 1) +
  xlab("Cumulative Lag") +
  ylab("Relative Risk") +
  scale_x_continuous(breaks = df_cum$cum_number) +
  geom_line(aes(y = 1), color = "red", lty = "dotted", size = 2) +
  ylim(1 - 0.0018, 1 + 0.0018) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 18), 
    axis.text.y = element_text(size = 18),
    axis.title = element_text(size = 20),
    legend.text = element_text(size = 18),
    legend.title = element_text(size = 20),
    plot.title = element_text(size = 20)
  )

ggsave("plots/plot_cum.png", width = 10, height = 10)

```

# Robustness
## Robustness: different df for spline around date
```{r}

pm2.5_cols <- grep("PM2\\.5", names(district_data), value = TRUE)

# different df for date spline
df_timespline <- c(10, 15, 20, 25, 50)

df_res_date <- data.frame(df = numeric(), 
                         variable = character(), 
                         coefficient = numeric(), 
                         std.error = numeric(), 
                         p_value = numeric(),
                         AIC = numeric(),
                         stringsAsFactors = FALSE)



k <- 1 # for iterations

for (j in seq_along(df_timespline)) {
  for (i in seq_along(pm2.5_cols)) {

    # Define model formula
    formulaCVD <- as.formula(paste0("CVD ~ ", pm2.5_cols[i],
                                    shortformulaCVD_wodate, "ns(date, ",
                                    df_timespline[j], ")"))
    
    # Fit model
    model_fit <- gamlss(formulaCVD, data = district_data, family = PO)
    
    model_summary <- summary(model_fit, save = T)
    
    df_res_date[k, "df"] <- df_timespline[j]
    df_res_date[k, "variable"] <- pm2.5_cols[i]
    df_res_date[k, "coefficient"] <- model_summary$coef[pm2.5_cols[i]]
    df_res_date[k, "std.error"] <- model_summary$se[pm2.5_cols[i]]
    df_res_date[k, "p_value"] <- model_summary$pvalue[pm2.5_cols[i]]
    df_res_date[k, "AIC"] <- model_fit$aic

     
    k <- k + 1
  }
}


```

##  Tables for date spline
```{r}
df_res_date <- df_res_date %>%
  mutate(variable = ifelse(variable == "PM2.5", "PM2.5_lag0", variable))

colnames(df_res_date)[1] <- "df of date-spline"
colnames(df_res_date)[3] <- "PM2.5 coefficient"


# for report
latex_date_cum <- df_res_date %>%
  filter(variable %in% c("PM2.5_lag0", "PM2.5_cum1", "PM2.5_cum2", "PM2.5_cum3",
                         "PM2.5_cum4", "PM2.5_cum5"))
latex_date_lag <- df_res_date %>%
  filter(variable %in% c("PM2.5_lag0", "PM2.5_lag1", "PM2.5_lag2", "PM2.5_lag3",
                         "PM2.5_lag4", "PM2.5_lag5"))

latex_date_lag$std.error <- NULL
latex_date_cum$std.error <- NULL


latex_date_lag <- xtable(latex_date_lag, digits = c(0, 0, 5, 5, 5, 1))
latex_date_cum <- xtable(latex_date_cum, digits = c(0, 0, 5, 5, 5, 1))


print.xtable(latex_date_lag, include.rownames = FALSE)
print.xtable(latex_date_cum, include.rownames = FALSE)

```


## Robustness: Non-Linearity of PM2.5

```{r}
pm2.5_cols <- grep("PM2\\.5", names(district_data), value = TRUE)

df_pmspline <- c(10)

df_res_pm <- data.frame(df = numeric(), 
                         variable = character(), 
                         coefficient = numeric(), 
                         std.error = numeric(), 
                         p_value = numeric(),
                         AIC = numeric(),
                         stringsAsFactors = FALSE)


k <- 1

for (j in seq_along(df_pmspline)) {
  for (i in seq_along(pm2.5_cols)) {

    # Define model formula
    formulaCVD <- 
      as.formula(paste0("CVD ~ ", "s(", pm2.5_cols[i], ", bs = 'ps', k = ", df_pmspline[j], ")", shortformulaCVD))
    
    # Fit model
    model_fit <- gam(formulaCVD, data = district_data, family = poisson)
    
    png(paste0("plots/spline_", pm2.5_cols[i], "_", "PM_spline", df_pmspline[j], ".png"), width = 480, height = 480)

    plot(model_fit, 
         ylim = c(-0.25, 0.25),
         xlab = paste0( pm2.5_cols[i], " Value"), xlim = c(0,280))
    
    dev.off()

    

  }
}
```


## Robustness: Capping
```{r}

# Capping PM2.5 values above 100 to 100
district_data_cap <- district_data %>%
  mutate(across(matches("^PM2\\.5"), ~ pmin(., 100)))

pm2.5_cols <- grep("PM2\\.5", names(district_data_cap), value = TRUE)

df_res_cap <- data.frame(
  variable = character(),
  coefficient = numeric(),
  std.error = numeric(),
  p_value = numeric(),
  AIC = numeric(),
  stringsAsFactors = FALSE
)


for (i in seq_along(pm2.5_cols)) {
  
  # Define formula with capped PM2.5 term
  formulaCVD <- as.formula(paste0("CVD ~ ", pm2.5_cols[i], shortformulaCVD))
  
  # Fit model
  model_fit <- gamlss(formulaCVD, data = district_data_cap, family = PO)
  
  model_summary <- summary(model_fit, save = T)
  
  df_res_cap[i, "variable"] <- pm2.5_cols[i]
  df_res_cap[i, "coefficient"] <- model_summary$coef[pm2.5_cols[i]]
  df_res_cap[i, "std.error"] <- model_summary$se[pm2.5_cols[i]]
  df_res_cap[i, "p_value"] <- model_summary$pvalue[pm2.5_cols[i]]
  df_res_cap[i, "AIC"] <- model_fit$aic
  
}

table_df_res_cap <- tableGrob(df_res_cap, rows = NULL)
ggsave("plots/table_df_res_cap.png", table_df_res_cap)

```


## Visualization Capping
```{r}

df_res_cap$RR <- exp(df_res_cap$coefficient)
df_res_cap$lower <- exp(df_res_cap$coefficient - 1.96 * df_res_cap$std.error)
df_res_cap$upper <- exp(df_res_cap$coefficient + 1.96 * df_res_cap$std.error)

# Filter for single lag terms
df_lags <- df_res_cap
df_lags[1, 1] <- "PM2.5_lag0"
df_lags <- df_lags[grep("lag", df_lags$variable),]

df_lags$lag_number <- as.numeric(gsub("PM2.5_lag", "", df_lags$variable))


ggplot(df_lags, aes(x = lag_number, y = RR)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .1, size = 1) +
  xlab("Lag") +
  ylab("Relative Risk") +
  scale_x_continuous(breaks = df_lags$lag_number) +
  geom_line(aes(y = 1), color = "red", lty = "dotted", size = 2) +
  ylim(1 - 0.0018, 1 + 0.0018) + 
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 18), 
    axis.text.y = element_text(size = 18),
    axis.title = element_text(size = 20),
    legend.text = element_text(size = 18),
    legend.title = element_text(size = 20),
    plot.title = element_text(size = 20)
  )

ggsave("plots/plot_lags_CAP.png", width = 10, height = 10)


# Filter for cumulative lag terms
df_cum <- df_res_cap
df_cum[1, 1] <- "PM2.5_cum0"
df_cum <- df_cum[grep("cum", df_cum$variable),]

df_cum$cum_number <- as.numeric(gsub("PM2.5_cum", "", df_cum$variable))

ggplot(df_cum, aes(x = cum_number, y = RR)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .1, size = 1) +
  xlab("Cumulative Lag") +
  ylab("Relative Risk") +
  scale_x_continuous(breaks = df_cum$cum_number) +
  geom_line(aes(y = 1), color = "red", lty = "dotted", size = 2) +
  ylim(1 - 0.0018, 1 + 0.0018) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 18), 
    axis.text.y = element_text(size = 18),
    axis.title = element_text(size = 20),
    legend.text = element_text(size = 18),
    legend.title = element_text(size = 20),
    plot.title = element_text(size = 20)
  )

ggsave("tables/plot_cum_CAP.png", width = 10, height = 10)


```


# Spatial Variation: one model per district
```{r}

pm2.5_cols <- grep("PM2\\.5", names(district_data), value = TRUE)

districts <- unique(district_data$districtID)

df_res_dis <- data.frame(district = character(), 
                         variable = character(), 
                         coefficient = numeric(), 
                         std.error = numeric(), 
                         p_value = numeric(),
                         AIC = numeric(),
                         stringsAsFactors = FALSE)


k <- 1 # for iteration

for (j in seq_along(districts)) {
  for (i in seq_along(pm2.5_cols)) {
    # Filter data for current district
    district_data_j <- filter(district_data, districtID == districts[j])
    
    # Define the model formula with PM2.5 term
    formulaCVD <- as.formula(paste0("CVD ~ ", pm2.5_cols[i], shortformulaCVD_wodis))
    
    # Fit model
    model_fit <- gamlss(formulaCVD, data = district_data_j, family = PO)
    
    model_summary <- summary(model_fit, save = T)
    
    df_res_dis[k, "district"] <- districts[j]
    df_res_dis[k, "variable"] <- pm2.5_cols[i]
    df_res_dis[k, "coefficient"] <- model_summary$coef[pm2.5_cols[i]]
    df_res_dis[k, "std.error"] <- model_summary$se[pm2.5_cols[i]]
    df_res_dis[k, "p_value"] <- model_summary$pvalue[pm2.5_cols[i]]
    df_res_dis[k, "AIC"] <- model_fit$aic
    
    k <- k + 1
  }
}


# only single lag-terms for largest and smallest district
table_df_res_dis <- df_res_dis %>%
  filter(district %in% c(2, 13) & !grepl("cum", variable))

table_df_res_dis <- tableGrob(table_df_res_dis, rows = NULL)
ggsave("tables/table_df_res_dis.png", table_df_res_dis)


```

## Visualization Spatial Variation
```{r}

mashhad_shape <- st_read("mashhad_shape")

# Define function to plot and save maps
plot_and_save_maps <- function(df_res_dis, mashhad_shape) {
  pm25_variables <- unique(df_res_dis$variable)

  for(pm25_var in pm25_variables) {
    df_filtered <- df_res_dis[df_res_dis$variable == pm25_var,]
    df_filtered$coefficient_exp <- exp(df_filtered$coefficient)
    merged_data <- merge(mashhad_shape, df_filtered, 
                         by.x = "District", by.y = "district")
    
    if(pm25_var == pm25_variables[1]) {pm25_var <- "PM2.5_lag0"}
    
    plot <- ggplot() +
      geom_sf(data = merged_data, aes(fill = coefficient_exp), color = "black") +
      scale_fill_gradient2(low = "blue", high = "red", midpoint = 1, 
                           limit = c(0.992, 1.008),
                           name = "Relative Risk") +
      geom_text(data = merged_data,
                aes(x = x, y = y, label = District), size = 6, 
                check_overlap = TRUE) +
      xlab(NULL) +  
      ylab(NULL) + 
      theme_minimal()+
      theme(
              axis.text = element_text(size = 18), 
              axis.title = element_text(size = 20),
              legend.text = element_text(size = 18),
              legend.title = element_text(size = 20),
              plot.title = element_text(size = 20)
    )
    
    
    ggsave(paste0("plots/spatial_", pm25_var, ".png"), plot, width = 10, height = 10)
    print(plot)
  }
}

plot_and_save_maps(df_res_dis, mashhad_shape)


```


# Extra: Subgroup Analysis
```{r}

pm2.5_cols <- grep("PM2\\.5", names(district_data), value = TRUE)

group <- c("above_age65", "below_age65") 

df_res_group <- data.frame(group = character(), 
                         variable = character(), 
                         coefficient = numeric(), 
                         std.error = numeric(), 
                         p_value = numeric(),
                         AIC = numeric(),
                         stringsAsFactors = FALSE)

k <- 1 # for iteration

for (j in seq_along(group)) {
  for (i in seq_along(pm2.5_cols)) {

    # Define model formula
    formulaCVD <- as.formula(paste0("CVD_", group[j], " ~ ", pm2.5_cols[i],
                                    shortformulaCVD_group, 
                                    "offset(log(pop_",group[j], "))"))
    
    # Fit model
    model_fit <- gamlss(formulaCVD, data = district_data, family = PO)
    
    model_summary <- summary(model_fit, save = T)
    
    df_res_group[k, "group"] <- group[j]
    df_res_group[k, "variable"] <- pm2.5_cols[i]
    df_res_group[k, "coefficient"] <- model_summary$coef[pm2.5_cols[i]]
    df_res_group[k, "std.error"] <- model_summary$se[pm2.5_cols[i]]
    df_res_group[k, "p_value"] <- model_summary$pvalue[pm2.5_cols[i]]
    df_res_group[k, "AIC"] <- model_fit$aic
    
    
    
    k <- k + 1
  }
}

# save table for PM2.5 lag0 and PM2.5 lag1
table_df_res_group <- df_res_group %>%
  filter(variable %in% pm2.5_cols[c(1,2)])

table_df_res_group <- tableGrob(table_df_res_group, rows = NULL)

ggsave("tables/table_df_res_group.png", table_df_res_group)

```


## Visualization Subgroup Analysis
```{r}

df_res_group$RR <- exp(df_res_group$coefficient)
df_res_group$lower <- exp(df_res_group$coefficient - 1.96 * df_res_group$std.error)
df_res_group$upper <- exp(df_res_group$coefficient + 1.96 * df_res_group$std.error)

# filter for single lag variables
df_lags <- df_res_group
df_lags[1, 1] <- "PM2.5_lag0"
df_lags <- df_lags[grep("lag", df_lags$variable),]

df_lags$lag_number <- as.numeric(gsub("PM2.5_lag", "", df_lags$variable))


# Plot
dodge_width = 0.25

ggplot(df_lags, aes(x = lag_number, y = RR, group = group, color = group)) +
  geom_point(position = position_dodge(width = dodge_width), size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .05, size = 1,
                position = position_dodge(width = dodge_width)) +
  xlab("Lag") +
  ylab("Relative Risk") +
  scale_x_continuous(breaks = unique(df_cum$cum_number)) +
  geom_hline(yintercept = 1, linetype = "dotted",color = "red", size = 2) +
  ylim(1 - 0.0018, 1 + 0.0018) +  
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 18), 
    axis.text.y = element_text(size = 18),
    axis.title = element_text(size = 20),
    legend.text = element_text(size = 18),
    legend.title = element_text(size = 20),
    plot.title = element_text(size = 20),
    legend.position = "bottom"
  )+
    scale_color_manual(name = "Group", labels = c(">=65 years", "<65 years"), 
                       values = c("darkgreen", "blue")) 

ggsave("plots/plot_lags_GROUP.png", width = 10, height = 10)


# Filter for cumulative lag terms
df_cum <- df_res_group
df_cum[1, 1] <- "PM2.5_cum0"
df_cum <- df_cum[grep("cum", df_cum$variable),]

df_cum$cum_number <- as.numeric(gsub("PM2.5_cum", "", df_cum$variable))

# Plot

ggplot(df_cum, aes(x = cum_number, y = RR, group = group, color = group)) +
  geom_point(position = position_dodge(width = dodge_width), size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .05, size = 1, 
                position = position_dodge(width = dodge_width)) +
  xlab("Cumulative Lag") +
  ylab("Relative Risk") +
  scale_x_continuous(breaks = unique(df_cum$cum_number)) +
  geom_hline(yintercept = 1, color = "red", linetype = "dotted", size = 2) +
  ylim(1 - 0.0018, 1 + 0.0018) +  
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 18), 
    axis.text.y = element_text(size = 18),
    axis.title = element_text(size = 20),
    legend.text = element_text(size = 18),
    legend.title = element_text(size = 20),
    plot.title = element_text(size = 20),
    legend.position = "bottom"
  )+
    scale_color_manual(name = "Group", labels = c(">=65 years", "<65 years"), 
                       values = c("darkgreen", "blue")) 



ggsave("plots/plot_cum_GROUP.png", width = 10, height = 10)


```


